Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-05-04 WSSSPE4_report/WSSSPE4_report.tex
removing note
minor edits to papers/demos section

\note{Sandra Gesing will write this}

WSSSPE included the presentation of 12 10-minute talks (based on four idea papers, three position papers,
two experience papers, and three demos) that addressed a wide range of topics around
sustainability for software in science. They covered three main areas:
\begin{enumerate}
\item The specifics of the academic environment for software development and for so-called
research programmers or research software engineers;
\item The characteristics and needs of research software in general such as the lifecycle of
software in science, preservation, curation, sharing, and reproducibility challenges; and
\item Lessons learned from or visions for use cases of scientific software and communities
working with and\slash or on a software package.
\end{enumerate}

@@

The following four papers belong to the first area, the academic environment. They address diverse aspects ranging from incentives for quality software to advocating a professional society for research software to roles and degrees for research software engineers. For talks with multiple authors, an \textsuperscript{\textasteriskcentered} indicates the author who presented the talk.

@@

The second main area, concerned with characteristics and needs of research software, includes the following five papers.

@@

Three contributions focused on the third main area, elucidating lessons learned from or visions for use cases of scientific software and communities working with and\slash or on a software package.

>>>>

%\note{Sandra Gesing will write this}

WSSSPE included the presentation of 12 10-minute talks (based on four idea papers, three position papers,
two experience papers, and three demos) that addressed a wide range of topics around
sustainability for software in science. These talks covered three main areas:
\begin{enumerate}
\item The specifics of the academic environment for software development and for so-called
research programmers or research software engineers;
\item The characteristics and needs of research software in general such as the lifecycle of
software in science, preservation, curation, sharing, and reproducibility challenges; and
\item Lessons learned from or visions for use cases of scientific software and communities
working with and\slash or on a software package.
\end{enumerate}

@@

The following four papers belong to the first area: the academic environment.
They address diverse aspects ranging from incentives for quality software to
dvocating a professional society for research software to roles and degrees for
research software engineers. For talks with multiple authors, an
\textsuperscript{\textasteriskcentered} indicates the author who presented the talk.

@@

The second main area, concerned with characteristics and needs of research software, includes the following five papers:

@@

Three contributions focused on the third main area: elucidating lessons learned
from or visions for use cases of scientific software and communities working
with and\slash or on a software package.
